The Bug Catalog of the Maven Ecosystem

### 2014-02-16 docs/msr.tex
updated data section

As we mentioned earlier our data was stored in a
Mongo{\sc db} database, thus all the data stored 
converted to the {\sc json} format. Originally, FindBugs output is in {\sc xml}, the conversion was a straight forward mapping
of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a metadata section, which contained
several additional information regarding the jar file that has been processed (Table~\ref{tbl:metadata-description}). The following listing contains a sample document:

@@

\begin{table}
\centering
\caption{Jar metadata description}
\label{tbl:metadata-description}
\begin{tabular}{l p{5.0cm}}
 \hline
\textbf{Key} & \textbf{Value}\\
 \hline
\verb|jar_filename| & JAR's filename\\
\verb|jar_size| & The size of the JAR file\\
\verb|version| & The version of the project in Maven repository\\
\verb|version_list| & A list of project's version numbers\\
\verb|artifact_id| & The artifact id of the project in Maven repository\\
\verb|group_id| & The group id of the project in Maven repository\\
\verb|dependencies| & List of all dependencies for the project\\
 \hline
 \end{tabular}
\end{table}

Hence, it is easy to either create
queries to find out basic information like:
``how many bad practice bugs exist in the repository", or
create scripts that can help us capture correlations
that could provide valuable findings.
Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
repository.

>>>>

As we mentioned earlier our data was stored in a
Mongo{\sc db} database, thus all the data were 
converted to the {\sc json} format. Originally, FindBugs output data is in {\sc xml} format. The conversion was a straight forward mapping
of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a metadata section, which contained
several additional information regarding the jar file that has been processed (Table~\ref{tbl:metadata-description}). The following listing contains an excerpt:

@@

Since Mongo{\sc db} provides a rich query interface, it was easy to either create
queries to find out basic information like:
``how many bad practice bugs exist in the repository", or
create scripts that can help us capture correlations
that could provide valuable findings. Figure~\ref{fig:bug-per} shows how software 
bugs are distributed among the repository.

\begin{table}
\centering
\caption{Jar metadata description}
\label{tbl:metadata-description}
\begin{tabular}{l p{5.0cm}}
 \hline
\verb|jar_filename| & JAR's filename\\
\verb|jar_size| & The size of the JAR file\\
\verb|version| & The version of the project in Maven repository\\
\verb|version_list| & A list of project's version numbers\\
\verb|artifact_id| & The artifact id of the project in Maven repository\\
\verb|group_id| & The group id of the project in Maven repository\\
\verb|dependencies| & List of all dependencies for the project\\
 \hline
 \end{tabular}
\end{table}
